\fakebf{HIV virulence evolution in structured epidemic models}

### 2016-05-31 poster/hivlhs_eeid2016.Rnw
further poster fussing

%\documentclass[final,hyperref={pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{ebgaramond}
\newcommand{\fakebf}{\fontfamily{mdugm}\fontseries{b}\selectfont}
%% reset default
\renewcommand{\rmdefault}{cmss}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

% http://tex.stackexchange.com/questions/13423/how-to-change-the-color-of-href-links-for-real
\hypersetup{colorlinks,linkcolor=}

@@

\author{\href{http://www.math.mcmaster.ca/bolker/}{Ben Bolker and Sang Woo Park}}
\email{\href{mailto:bolker@mcmaster.ca}{\texttt{bolker@mcmaster.ca}}}
\institute[McMaster University]{McMaster University, Hamilton, Ontario, Canada 
%%\\\vspace{5mm}\texttt{earn@math.mcmaster.ca}
}
%\institute[]{}
\date[June 2016]{June 2016}

%% Uncomment the following line to define a custom logo (or to tweak the size of the logo)
\DrexelLogo{\includegraphics[width=\WhenPortrait{1.75}{1}\linewidth]{images/Maclogo}}

@@

\begin{itemize}
\item virulence evolution mediated by transmission-vs-clearance tradeoff
\item still debated \cite{EbertBull2003,alizon_adaptive_2015}
\item HIV \cite{fraser_virulence_2014}: \textbf{set-point viral load}
      correlated with transmission probability, rate of progression to AIDS (data from Rakai, Uganda)
\item eco-evolutionary virulence dynamics: \cite{shirreff_transmission_2011}
\end{itemize}

@@

\textbf{infection} from (1) inf. partner (discordant couples);
(2) other coupled inf.; (3) uncoupled inf.

\vspace{0.2cm}
Model choices:
\begin{itemize}
\item \textbf{pair formation}: instantaneous or delayed?
\item \textbf{extra-pair contact} (epc): present or absent?
\item \textbf{implicit model}: no explicit partnerships,
  force of infection expression derived from $\Ro$ of pair-formation
  model (without epc)
\item \textbf{random-mixing model}: standard SIR model
\end{itemize}

@@

\begin{block}{Sampling strategy}
% https://www.sharelatex.com/learn/Wrapping_text_around_figures
  \setlength{\abovecaptionskip}{0pt}
  \setlength{\belowcaptionskip}{0pt}
  \setlength{\intextsep}{0pt}
  \setlength{\textfloatsep}{0pt}
% \begin{wrapfigure}{l}{0.6\textwidth}
%%\begin{columns}
%%  \begin{column{0.5
%%\begin{center}

@@

\begin{itemize}
\item significant variation across model structures
\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
\item implicit model is \textbf{most different}
\item random-mixing model underestimates (?) variability
\end{itemize}

@@

              \vspace{1cm}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
            \end{block}
            \vspace{0.5cm}

@@

\begin{itemize}
\item Random-mixing models gave the closest match to the most realistic models; extra-pair contact washed out the effects
of epidemiological structure
\item Variation among models (model structure) $\approx$ variation within models (parameter uncertainty)
\item Large differences
in evolutionary dynamics among different epidemiological models
suggest caution in predicting evolutionary responses
\end{itemize}

@@

We thank Christophe Fraser for providing access to code, and 
the Natural Sciences and Engineering Research Council of Canada (NSERC)
for funding.

>>>>

%\documentclass[final,hyperref={hidelinks,pdfpagelabels=false}]{beamer}
\documentclass{beamer}
\usepackage{ebgaramond}
\newcommand{\fakebf}{\fontfamily{mdugm}\fontseries{b}\selectfont}
%% reset default
\renewcommand{\rmdefault}{cmss}
\usepackage{grffile}
\mode<presentation>{\usetheme{mcmaster}}

@@

% http://tex.stackexchange.com/questions/13423/how-to-change-the-color-of-href-links-for-real
\hypersetup{hidelinks}

@@

\author{\fakebf\href{http://www.math.mcmaster.ca/bolker/}{Ben Bolker and Sang Woo Park}}
\email{\href{mailto:bolker@mcmaster.ca}{\texttt{bolker@mcmaster.ca}}}
%% URL for project (footer)
\projurl{\texttt{https://github.com/bbolker/HIV\_LHS/}}
\institute[McMaster University]{McMaster University, Hamilton, Ontario, Canada 
%%\\\vspace{5mm}\texttt{earn@math.mcmaster.ca}
}
%\institute[]{}
\date[June 2016]{June 2016}

%% Uncomment the following line to define a custom logo (or to tweak the size of the logo)
\McMasterLogo{\includegraphics[width=\WhenPortrait{1.75}{1}\linewidth]{images/Maclogo}}

@@

\begin{itemize}
\item virulence evolution mediated by transmission-vs-clearance tradeoff
\item still debated \cite{EbertBull2003,alizon_adaptive_2015}
\item HIV \cite{fraser_virulence_2014}: \textbf{set-point viral load} ($\approx$ ``virulence'')
      correlated with transmission probability, rate of progression to AIDS (data from Rakai, Uganda)
\item eco-evolutionary virulence dynamics: \cite{shirreff_transmission_2011}
\end{itemize}

@@

\textbf{infection} from (1) infected partner ($SI$ couples);
(2) other coupled inf.; (3) uncoupled inf.

\vspace{0.4cm}

\begin{itemize}
\item \textbf{pair formation}: instantaneous or delayed?
\item \textbf{extra-pair contact} (epc): present or absent?
\item \textbf{implicit model}: no explicit partnerships,
  force of infection expression derived from $\Ro$ of pair-formation
  model (without epc)
\item \textbf{random-mixing model}: standard SIR model
\end{itemize}

@@

\begin{block}{Parameter uncertainty/exploration}
% https://www.sharelatex.com/learn/Wrapping_text_around_figures
  \setlength{\abovecaptionskip}{0pt}
  \setlength{\belowcaptionskip}{0pt}
  \setlength{\intextsep}{0pt}
  \setlength{\textfloatsep}{0pt}
% \begin{wrapfigure}{l}{0.6\textwidth}
%%\begin{columns}
%%  \begin{column{0.5
%%\begin{center}

@@

\begin{itemize}

\item least (random) and most (pairform+epc) models \textbf{most similar}:
  single individuals and extra-pair contact wash out effects of structure
\item implicit model is \textbf{most different}
\item random-mixing model underestimates variability
\end{itemize}

@@

              \vspace{1cm}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
\begin{itemize}
\item peak timing: epc $>$ finite pair-formation effects
\item equilibrium virulence: interaction
\item low-equilibrium outcomes for intermediate-complexity models
\end{itemize}

            \end{block}
            \vspace{0.5cm}

@@

\begin{itemize}
\item Random-mixing models best matched the most realistic models; extra-pair and uncoupled individuals washed out the effects
of epidemiological structure
\item Implicit models did worst
\item Variation among models (model structure) $\approx$ variation within models (parameter uncertainty)
\item Large differences
in evolutionary dynamics among different epidemiological models
$\to$ caution in predicting evolutionary responses
\item \textbf{neglected:} disease life history details, sex workers, age-structured mixing \dots
agent-based models?
\end{itemize}

@@

We thank C. Fraser and D. Champredon for code access and 
the Natural Sciences and Engineering Research Council of Canada (NSERC)
for funding.
